---
title: "R Markdown"
date: "August 18, 2016"
output: 
  html_notebook
  # ioslides_presentation:
    # logo: logo.png

---
WOOOOOhOOOOOO
  .title-slide {
    }
  slide {
    background-color:white;
    }
  slides > slide:not(.nobackground):before {
    width: 200px;
    height: 18px;
    background-size: 200px 18px;
    }
    
</style>

```{r setup, include=FALSE}
library(knitr)
library('ggplot2')
library(dplyr)

knitr::opts_chunk$set(echo = FALSE)
knitr::knit_engines$set('python')
```

## R Markdown  

Rmd is a format for writing reproducible and dynamic reports with R.



Cheat sheets and reference pages can be found on RStudio website

[Rmd Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)

[Rmd Reference Sheet](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf)

[CSS Default](https://github.com/rstudio/rmarkdown/blob/master/inst/rmd/ioslides/ioslides-13.5.1/theme/css/default.css)

## Best Used For

- Documentation 
- Reports
- Presentations
- RODB -> SQL queries 
- Interactive Notebook



## Rendered Document Types

- HTML 
- HTML notebook (interactive like Jupyter or Zeppelin) NEW!!!
- PDF
- word 
- md 
- slides (isoslides, beamer, slidy)

## Useful Tools

- Creating Tables
- Images
- Hyperlinks 
- $\LaTeX$
- Itemized lists
- Code chunk options (running, supress warnings, display, code decoration)
- Inline code
- HTML widgets - allow interactive plots (dygraph, d3heatmaps, shiny)




## Different Languages in Rmd
You can additionally start writing code by changing the engine to the language of choice. Default language is set to R.


```{r different_langaguages, echo = TRUE}
names(knitr::knit_engines$get()) 
```

## Python in Rmd

```{python, echo = TRUE}
x = 'jaclyn'
h = 'Hello, '
print h + x

```


## Bringing in Data

```{r, echo = FALSE}
# echo = FALSE
head(pressure)
```

## Bringing in Data w/ Code

```{r, echo =TRUE}
# echo = TRUE
head(pressure)
```


## Slide with Plot

```{r}
plot(pressure)
```


## Downloading R Notebook

devtools::install_github("rstudio/rmarkdown")

Benefits: Version Control with retained output .Rproj.user



